Maximising the guaranteed feasible set for uncertain MPC schemes with chance constraints

### 2016-11-07 draft.tex

\section{Approximating the guaranteed $n$-step controllable set}\label{ssec:approximating:n:step}
%
We now turn our attention to the $n$-step controllable set~$\C_n(\T)$ for a given target set~$\T$.
%
This is defined as the set of initial conditions $x_0\in\X$ such that a sequence of control inputs exists that drives the state in $n$ steps to the target set, so that $x_n\in\T$ for all admissible disturbance sequences 
$w_k\in\W$, $k=0,\ldots,n-1$, while guaranteeing that the robust state and input constraints 
%$x_k\in\X$, $u_k\in\U$
(\ref{eq:state_input:constraints}) and the probabilistic constraint~(\ref{eq:probabilistic:constraint}) are satisfied.
%
Thus $\C_n(\T)$ can be expressed as follows.
%
\begin{multline*}
\C_n(\T) = \Bigl\{x_0\in\X: \exists \bigl\{u_0(\cdot),\ldots,u_{n-1}(\cdot)\bigr\}\\
\begin{aligned}
&x_{k+1} = A^{k+1} x_0 + \sum_{i=0}^{k} A^{k-i}B u_{i}(x_{i}) + \sum_{i=0}^{k} A^{k-i} w_{i}\\
&x_n\in\T\\
&x_{k+1}\in\X\\
&u_k(x_k)\in\U\\
&\PP\bigl\{v\in\V : Cx_k + Du_k(x_k) +v \in\Y\bigr\}\geq p
\end{aligned}\\
\forall w_k\in\W,\, \forall k\in\{ 0, \ldots , n-1\} \Bigr\}	
\end{multline*}
% \begin{equation}
% 	\C_n(\T) = \left\{x\in\X:\begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
% 	&x_N\in\T\\
% 	&x_k\in\X\\
% 	&\PP\{(C+DK)x_k+v\in\Y\}\geq p\\
% 	&\forall w_j\in\W,k\geq 0\end{aligned} \right\}	
% \end{equation}
%
Using Proposition~\ref{prop1} it is easy to verify that the set $C_n(\T)$ defined by
%
\begin{multline*}
C_n(\T) = \Bigl\{ x_0\in\X: \exists \bigl\{u_0(\cdot),\ldots,u_{n-1}(\cdot)\bigr\}\\
\begin{aligned}
&x_{k+1} = A^{k+1} x_0 + \sum_{i=1}^{k} A^{k-i}B u_{i}(x_{i}) + \sum_{i=1}^{k} A^{k-i} w_{i}\\
&x_N\in\T\\
&x_{k+1}\in\X\\
&u_k(x_k)\in\U \\
&Cx_k+Du_k(x_k) + v_k \in\Y
\end{aligned}\\
\forall w_k\in\W,\, \forall v_k\in \V^\prime,\, \forall k\in\{0,\dots,n-1\} \Bigr\}	
\end{multline*}
% \begin{equation}
% 	C_n(\T) = \left\{x\in\X:\begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
% 	&x_N\in\T\\
% 	&x_k\in\X\\
% 	&(C+DK)x_k+v\in\Y\\
% 	&\forall w_j\in\W,v\in \V^\prime,k\in\{0,\dots,N\}\end{aligned} \right\}	
% \end{equation}
%
is necessarily contained in $\C_n(\T)$ for any $\V^\prime\subseteq\V$ with probability measure $\PP\{\V^\prime\} \geq p$.
%
As in the case of positively invariant sets, fixing $\V^\prime$ to be a polytopic set leads to a computationally tractable optimisation for the maximisation of~$C_n$. This suggests an algorithm for constructing $C_n$ as a polytopic approximation of~$\C_n$ by optimising~$\V^\prime$ so as to maximise the volume of~$C_n$.
% indirectly improves the approximation of $\C_n$.
%
It is known that 
%$C_n(\T) = C^n_1(\T) \doteq C_1(C_1(\cdots C_1(\T)\cdots))$ 
$C_n(\T) = C^n_1(\T) \doteq C_1 \circ C_1 \circ \cdots \circ C_1(\T)$ 
\citep[see e.g.][]{blanchini:2007}, which allows the use of simple computational geometry algorithms.

In particular, the one-step controllable set $C_1(\T)$ for the target set 
\[
\T = \Bigl\{x\in\RR^d : J_i x\leq1,\ i\leq M_\T\Bigr\}
\]
is given by the projection of
$L_1(\T)\subset \RR^{d+q_{\U}}$, 
%$L_1(\T)\subset \RR^d\times \RR^{q_{\U}}$, 
defined by
%
\begin{multline*}
L_1(\T) = \Bigl\{(x,u)\in (\X,\U): \\
\begin{aligned}
& Cx+Du + v\in\Y \\
& Ax+Bu+w\in\T
\end{aligned}\\
\forall v\in\V^\prime,\, \forall w\in\W\Bigr\} ,
%\end{aligned}
\end{multline*}
% \begin{equation}
% 	L_1(\T) = \left\{(x,u):\begin{aligned}
% 	x\in\X, u\in\U, Cx+Du + v\in\Y\;\forall v\in\V^\prime,\\
% 	Ax+Bu+w\in\T\;\forall w\in\W
% 	\end{aligned}\right\}
% \end{equation}
%
onto the $x$-subspace.
%
Thus
\[
C_1(\T) = \{ x : \exists u \ \text{such that} \ (x,u)\in L_1(\T)\}.
\]
As all involved sets are polytopic, $L_1(\T)$ is polytopic and its exact projection can be determined computationally.

@@

Analogously, \eqref{seq:optimisation:n:step:set:abstract} can be restated as
%
\begin{subequations}\label{seq:optimisation:n:step:precise}
\begin{equation}
	\max_{v_0,t_1,\dots,t_d} \vol(C_n(\T))
\end{equation}
subject to
\begin{equation}\label{eq:containment:linear:2}
	\Gamma\Bigl( (t_1v_1,\dots,t_dv_d)\lambda_i+v_0\Bigr)\leq \bfa{1}, \ i\leq 2^d 
%\Leftrightarrow \V^\prime\subseteq\V
\end{equation}
%
\begin{equation}\label{eq:measure:p:2}
	\prod_{i=1}^d t_i\geq p \frac{\vol(\V)}{\abs{\det(v_1,\dots,v_d)}} 
%\Leftrightarrow \frac{\vol(\V^\prime)}{\vol(\V)}\geq p
\end{equation}
%
\begin{equation}\label{eq:linear:inequalites:on:t:2}
	0<t_i\leq1, \ i\leq d.
\end{equation}
\end{subequations}
%

Note that~\eqref{eq:containment:linear:1} and~\eqref{eq:linear:inequalites:on:t:1} are linear constraints on $v_0$ and $t_i$, furthermore recall that $\prod_i t_i \geq c$, for constant $c$, is convex for $t_i>0$, so that the constraints in~(\ref{seq:optimisation:MRPI:precise}a-d) and~(\ref{seq:optimisation:n:step:precise}a-d) are convex.
%
Note also that the constraints (\ref{eq:containment:linear:1}) and (\ref{eq:containment:linear:2}) are equivalent to
\[
\V^\prime\subseteq\V ,
\]
whereas the constraints (\ref{eq:measure:p:1}) and (\ref{eq:measure:p:2}) are equivalent to
\[
\frac{\vol(\V^\prime)}{\vol(\V)}\geq p.
\]
%
However, the uniqueness of a maximiser for the volume in the objective functions (\ref{seq:optimisation:MRPI:precise}a) and (\ref{seq:optimisation:n:step:precise}a) is less transparent and cannot be guaranteed in general.

@@

In order to compare the proposed method with existing results we compute a sample-based set as described in~\cite{Zhang2015}, that is we compute the smallest set $\V^\prime$ containing enough samples to guarantee constraint satisfaction with a confidence of $1-\beta$.
%
To obtain a comparable result we use again use a scaled version of $\V$, so that the optimisation~\citep[eq.~(10)]{Zhang2015} is given as
%
\begin{subequations}\label{eq:comparison:set}
\begin{equation}\min_{\gamma_1,\dots,\gamma_4} \  \ \sum_{i=1}^4\gamma_i
\end{equation}
subject to 
\begin{equation}
\Gamma_i \hat{v}^{(j)}\leq \gamma_i ,\ i\in\{1,\ldots,4\}, \ j = 1,\ldots,N
\end{equation}
\end{subequations}
% \begin{equation}\label{eq:comparison:set}\begin{split}
% 	\min_{\gamma_1,\dots,\gamma_4}&\quad\sum_{i=1}^4\gamma_i\\
% 	\text{s.t.}&\quad \Gamma_i \bfa{v}^{(j)}\leq \gamma_i ,i\in\{1,\dots,4\}
% \end{split}\end{equation}
%
Where $\V = \{v : \Gamma_i v \leq 1, \, i =1, \ldots ,4\}$ and
%$\hat{v}^{(j)}$, $j=1,\ldots,N$ 
$\hat{v}^{(1)},\ldots,\hat{v}^{(N)}$
are the samples used to satisfy the probabilistic requirements with the given confidence of $\beta=0.001$. The number of samples that are needed to satisfy this requirement is given by the cumulative binomial distribution, but can be overestimated to be $N \geq \frac{2}{\beta}(2-\log(p))$, so for this example $N = 4714$.
%
The resulting sets are illustrated in Figure~\ref{fig:MRPI:optimised}.
%

\begin{figure}
\includegraphics[width=.95\linewidth]{MRPIsetOptimised.pdf}
\caption{The guaranteed positively invariant set $X^\infty$ computed using~(\ref{seq:optimisation:MRPI:abstract}a-c) 
%of the system~\eqref{eq:example:system:MRPI} 
in red, and in blue the robust positively invariant set for the disturbance set computed using the methods discussed in~\cite{Zhang2015} with 
%a confidence level of $0.999$.}
confidence $1-\beta$, $\beta = 0.001$.}
\label{fig:MRPI:optimised}
\vspace{4mm}\end{figure}

For the same system and constraints (\ref{eq:example:system:MRPI})-(\ref{eq:example:pconstriaint}) we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=\{x:\norm{x}_\infty\leq 2\}$
%
by solving (\ref{seq:optimisation:n:step:set:abstract}a-c) for $C_1(\T)$, $C_2(\T)$, $C_3(\T)$.
%
Again the result illustrated in Figure~\ref{fig:n:step:controllable:set} is reproduced using different initial values although the Hessian at the maximiser has a non-trivial nullspace.
%

\begin{figure}
\includegraphics[width=.95\linewidth]{NStepSetOptimised.pdf}
\caption{Approximation of the guaranteed 3-step controllable set for a box $\T$ (in blue). Sets $C_1(\T)$, $C_2(\T)$ and $C_3(\T)$ computed by optimising $\V^\prime$ using  (\ref{seq:optimisation:n:step:set:abstract}a-c) are shown in solid lines. For comparison, the controllable sets obtained with~\eqref{eq:comparison:set} with 
confidence $1-\beta$, $\beta = 0.001$ are shown in dashed lines.}
\label{fig:n:step:controllable:set}
\vspace{4mm}\end{figure}

\section{Conclusions and future work}\label{sec:conclusion}
%
%
In this paper we present methods for approximating the positively invariant set and the $n$-step controllable set of a chance constrained stochastic system.
%
The approach we present is based on a simple restriction of the set $\V^\prime$ to be a parallelotope; this yields remarkable results in simulations and avoids the introduction of non-convex constraints in the optimisation problems (\ref{seq:optimisation:MRPI:abstract}a-c) and \mbox{(\ref{seq:optimisation:n:step:set:abstract}a-c)}.
 %

>>>>

\section{Approximating the guaranteed $n$-step controllable set}\label{ssec:approximating:n:step}
%
We now turn our attention to the $n$-step controllable set~$\C_n(\T)$ for a given target set~$\T$.
%
That is the set of initial conditions $x_0\in\C_n(\T)$ such that a sequence of control inputs exists that drives the state in $n$ steps to the target set, $x_n\in\T$, for all admissible disturbance sequences 
$w\in\W$, while guaranteeing that the robust state and input constraints~(\ref{eq:state_input:constraints}) and the probabilistic constraint~(\ref{eq:probabilistic:constraint}) are satisfied.
%
This is defined as the set of initial conditions $x_0\in\X$ such that a sequence of control inputs exists that drives the state in $n$ steps to the target set, so that $x_n\in\T$ for all admissible disturbance sequences 
$w_k\in\W$, $k=0,\ldots,n-1$, while guaranteeing that the robust state and input constraints 
%$x_k\in\X$, $u_k\in\U$
(\ref{eq:state_input:constraints}) and the probabilistic constraint~(\ref{eq:probabilistic:constraint}) are satisfied.
%
Thus $\C_n(\T)$ can be expressed as follows.
%
\begin{multline*}
\C_n(\T) = \Bigl\{x_0\in\X: \exists \bigl\{u_0(\cdot),\ldots,u_{n-1}(\cdot)\bigr\}\\
\begin{aligned}
&x_{k+1} = A^{k+1} x_0 + \sum_{i=0}^{k} A^{k-i}B u_{i}(x_{i}) + \sum_{i=0}^{k} A^{k-i} w_{i}\\
&x_n\in\T\\
&x_{k+1}\in\X\\
&u_k(x_k)\in\U\\
&\PP\bigl\{v\in\V : Cx_k + Du_k(x_k) +v \in\Y\bigr\}\geq p
\end{aligned}\\
\forall w_k\in\W,\, \forall k\in\{ 0, \ldots , n-1\} \Bigr\}	
\end{multline*}
% \begin{equation}
% 	\C_n(\T) = \left\{x\in\X:\begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
% 	&x_N\in\T\\
% 	&x_k\in\X\\
% 	&\PP\{(C+DK)x_k+v\in\Y\}\geq p\\
% 	&\forall w_j\in\W,k\geq 0\end{aligned} \right\}	
% \end{equation}
%
Using Proposition~\ref{prop1} it is easy to verify that the set $C_n(\T)$ defined by
%
\begin{multline*}
C_n(\T) = \Bigl\{ x_0\in\X: \exists \bigl\{u_0(\cdot),\ldots,u_{n-1}(\cdot)\bigr\}\\
\begin{aligned}
&x_{k+1} = A^{k+1} x_0 + \sum_{i=1}^{k} A^{k-i}B u_{i}(x_{i}) + \sum_{i=1}^{k} A^{k-i} w_{i}\\
&x_N\in\T\\
&x_{k+1}\in\X\\
&u_k(x_k)\in\U \\
&Cx_k+Du_k(x_k) + v_k \in\Y
\end{aligned}\\
\forall w_k\in\W,\, \forall v_k\in \V^\prime,\, \forall k\in\{0,\dots,n-1\} \Bigr\}	
\end{multline*}
% \begin{equation}
% 	C_n(\T) = \left\{x\in\X:\begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
% 	&x_N\in\T\\
% 	&x_k\in\X\\
% 	&(C+DK)x_k+v\in\Y\\
% 	&\forall w_j\in\W,v\in \V^\prime,k\in\{0,\dots,N\}\end{aligned} \right\}	
% \end{equation}
%
is necessarily contained in $\C_n(\T)$ for any $\V^\prime\subseteq\V$ with probability measure $\PP\{\V^\prime\} \geq p$.
%
As in the case of positively invariant sets, fixing $\V^\prime$ to be a polytopic set leads to a computationally tractable optimisation for the maximisation of~$C_n$. This suggests an algorithm for constructing $C_n$ as a polytopic approximation of~$\C_n$ by optimising~$\V^\prime$ so as to maximise the volume of~$C_n$.
% indirectly improves the approximation of $\C_n$.
%
It is known that 
%$C_n(\T) = C^n_1(\T) \doteq C_1(C_1(\cdots C_1(\T)\cdots))$ 
$C_n(\T) = C^n_1(\T) \doteq C_1 \circ C_1 \circ \cdots \circ C_1(\T)$ 
\citep[see e.g.][]{blanchini:2007}, which allows the use of simple computational geometry algorithms.

In particular the one-step controllable set $C_1(\T)$ for a polytopic~$\T$
% \[
% \T = \Bigl\{x\in\RR^d : J_i x\leq1,\ i\leq M_\T\Bigr\}
% \]
is given by the projection of 
%
In particular, the one-step controllable set $C_1(\T)$ for the polytopic target set~$\T$
% \[
% \T = \Bigl\{x\in\RR^d : J_i x\leq1,\ i\leq M_\T\Bigr\}
% \]
is given by the projection of
$L_1(\T)\subset \RR^{d+q_{\U}}$, 
%$L_1(\T)\subset \RR^d\times \RR^{q_{\U}}$, 
defined by
%
\begin{multline*}
L_1(\T) = \Bigl\{(x,u)\in (\X,\U): \\
\begin{aligned}
& Cx+Du + v\in\Y \\
& Ax+Bu+w\in\T
\end{aligned}\\
\forall v\in\V^\prime,\, \forall w\in\W\Bigr\} ,
%\end{aligned}
\end{multline*}
% \begin{equation}
% 	L_1(\T) = \left\{(x,u):\begin{aligned}
% 	x\in\X, u\in\U, Cx+Du + v\in\Y\;\forall v\in\V^\prime,\\
% 	Ax+Bu+w\in\T\;\forall w\in\W
% 	\end{aligned}\right\}
% \end{equation}
%
onto the $x$-subspace.
%
Thus
\[
C_1(\T) = \{ x : \exists u \ \text{such that} \ (x,u)\in L_1(\T)\}.
\]
As all involved sets are polytopic, $L_1(\T)$ is polytopic and its exact projection can be determined computationally.

@@

Analogously, \eqref{seq:optimisation:n:step:set:abstract} can be restated as
%
\begin{subequations}\label{seq:optimisation:n:step:precise}
\begin{equation}
	\max_{v_0,t_1,\dots,t_d} \vol(C_n(\T))
\end{equation}
subject to
\begin{equation}\label{eq:containment:linear:2}
	\Gamma\Bigl( (t_1v_1,\dots,t_dv_d)\lambda_i+v_0\Bigr)\leq \bfa{1}, \ i\leq 2^d 
%\Leftrightarrow \V^\prime\subseteq\V
\end{equation}
%
\begin{equation}\label{eq:measure:p:2}
	\prod_{i=1}^d t_i\geq p \frac{\vol(\V)}{\abs{\det(v_1,\dots,v_d)}} 
%\Leftrightarrow \frac{\vol(\V^\prime)}{\vol(\V)}\geq p
\end{equation}
%
\begin{equation}\label{eq:linear:inequalites:on:t:2}
	0<t_i\leq1, \ i\leq d.
\end{equation}
\end{subequations}
%
Note that~\eqref{eq:containment:linear:1} and~\eqref{eq:linear:inequalites:on:t:1} are linear constraints on $v_0$ and $t_i$, furthermore recall that $\prod_i t_i \geq c$, for a constant $c$, is convex for $t_i>0$, so that the constraints in~\eqref{seq:optimisation:MRPI:precise} and~\eqref{seq:optimisation:n:step:precise} are convex.
%
Note that~\eqref{eq:containment:linear:1} and~\eqref{eq:linear:inequalites:on:t:1} are linear constraints on $v_0$ and $t_i$, furthermore recall that $\prod_i t_i \geq c$, for constant $c$, is convex for $t_i>0$, so that the constraints in~(\ref{seq:optimisation:MRPI:precise}a-d) and~(\ref{seq:optimisation:n:step:precise}a-d) are convex.
%
Note also that the constraints (\ref{eq:containment:linear:1}) and (\ref{eq:containment:linear:2}) are equivalent to
\[
\V^\prime\subseteq\V ,
\]
whereas the constraints (\ref{eq:measure:p:1}) and (\ref{eq:measure:p:2}) are equivalent to
\[
\frac{\vol(\V^\prime)}{\vol(\V)}\geq p.
\]
%
However, the uniqueness of a maximiser for the volume in the objective functions (\ref{seq:optimisation:MRPI:precise}a) and (\ref{seq:optimisation:n:step:precise}a) is less transparent and cannot be guaranteed in general.

@@

In order to compare the proposed method with existing results we compute a sample-based set as described in~\cite{Zhang2015}, that is we compute the smallest set $\V^\prime$ containing enough samples to guarantee constraint satisfaction with a confidence of $1-\beta$.
%
To obtain a comparable result we use again use a scaled version of $\V$, so that the optimisation~\citep[eq.~(10)]{Zhang2015} is given as
%
\begin{subequations}\label{eq:comparison:set}
\begin{equation}\min_{\gamma_1,\dots,\gamma_4} \  \ \sum_{i=1}^4\gamma_i
\end{equation}
subject to 
\begin{equation}
\Gamma_i \hat{v}^{(j)}\leq \gamma_i ,\ i\in\{1,\ldots,4\}, \ j = 1,\ldots,N
\end{equation}
\end{subequations}
% \begin{equation}\label{eq:comparison:set}\begin{split}
% 	\min_{\gamma_1,\dots,\gamma_4}&\quad\sum_{i=1}^4\gamma_i\\
% 	\text{s.t.}&\quad \Gamma_i \bfa{v}^{(j)}\leq \gamma_i ,i\in\{1,\dots,4\}
% \end{split}\end{equation}
%
Where $\V = \{v : \Gamma_i v \leq 1, \, i =1, \ldots ,4\}$ and
%$\hat{v}^{(j)}$, $j=1,\ldots,N$ 
$\hat{v}^{(1)},\ldots,\hat{v}^{(N)}$
are the samples used to satisfy the probabilistic requirements with the given confidence of $\beta=0.001$. The number of samples that are needed to satisfy this requirement is given by the cumulative binomial distribution, but can be overestimated to be $N \geq \frac{2}{\beta}(2-\log(p))$, so for this example $N = 4714$.
%
The resulting sets are illustrated in Figure~\ref{figure:V:prime:and:comparison} and~\ref{fig:MRPI:optimised}.
%
\begin{figure}
\includegraphics[width=.95\linewidth]{Vprime.pdf}
\caption{The set~$\V^\prime$ resulting the optimisation~\eqref{seq:optimisation:MRPI:precise} for the discussed requirements in \textcolor[rgb]{0.9255,0.6902,0.2078}{yellow} with $\PP\{v\in\V^\prime\}=0.3$, and in \textcolor{red}{red}, the set satisfying~\eqref{eq:comparison:set}, with the defining samples. The comparison set contains $99.91$\% of the total volume of $\V$.}
\label{figure:V:prime:and:comparison}
\vspace{4mm}
\end{figure}

\begin{figure}
\includegraphics[width=.95\linewidth]{MRPIsetOptimised.pdf}
% \caption{The guaranteed positively invariant set of the system~\eqref{eq:example:system:MRPI} in solid red, in dashed blue the robust positively invariant set for the disturbance set computed with the methods discussed in~\cite{Zhang2015}.}
\caption{The guaranteed positively invariant set $X^\infty$ computed using~(\ref{seq:optimisation:MRPI:abstract}a-c) 
%of the system~\eqref{eq:example:system:MRPI} 
in red, and in blue the robust positively invariant set for the disturbance set computed using the methods discussed in~\cite{Zhang2015} with 
%a confidence level of $0.999$.}
confidence $1-\beta$, $\beta = 0.001$.}
\label{fig:MRPI:optimised}
\vspace{4mm}\end{figure}

For the same setup~\eqref{eq:example:system:MRPI} we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=X^\infty$.
%
Again the result illustrated in Figure~\ref{fig:n:step:controllable:set} can be reproduced using different initial values although the Hessian at the maximiser has a non-trivial nullspace.
%
For the same system and constraints (\ref{eq:example:system:MRPI})-(\ref{eq:example:pconstriaint}) we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=\{x:\norm{x}_\infty\leq 2\}$
%
by solving (\ref{seq:optimisation:n:step:set:abstract}a-c) for $C_1(\T)$, $C_2(\T)$, $C_3(\T)$.
%
Again the result illustrated in Figure~\ref{fig:n:step:controllable:set} is reproduced using different initial values although the Hessian at the maximiser has a non-trivial nullspace.
%

\begin{figure}
\includegraphics[width=.95\linewidth]{NStepSetOptimised.pdf}
% \caption{Approximation of the guaranteed 3-step controllable set for a guaranteed positive invariant set $X^\infty$ (in blue). The additional sets are remaining $C_1(X^\infty),C_2(X^\infty)$ and $C_3(X^\infty)$ dashed for the comparison set obtained with~\eqref{eq:comparison:set} and solid for the optimised~$\V^\prime$ obtained with the proposed method.}
\caption{Approximation of the guaranteed 3-step controllable set for a box $\T$ (in blue). Sets $C_1(\T)$, $C_2(\T)$ and $C_3(\T)$ computed by optimising $\V^\prime$ using  (\ref{seq:optimisation:n:step:set:abstract}a-c) are shown in solid lines. For comparison, the controllable sets obtained with~\eqref{eq:comparison:set} with 
confidence $1-\beta$, $\beta = 0.001$ are shown in dashed lines.}
\label{fig:n:step:controllable:set}
\vspace{4mm}\end{figure}

\section{Conclusions and future work}\label{sec:conclusion}
%
%
In this paper we present methods for approximating the positively invariant set and the $n$-step controllable set of a chance constrained stochastic system.
%
The method we present is based on a simple restriction of the set $\V^\prime\subseteq\V$ to be a parallelotope, which yields remarkable results in simulation and does not introduce non-convex constraints in the optimisation presented.
%
The approach we present is based on a simple restriction of the set $\V^\prime$ to be a parallelotope; this yields remarkable results in simulations and avoids the introduction of non-convex constraints in the optimisation problems (\ref{seq:optimisation:MRPI:abstract}a-c) and \mbox{(\ref{seq:optimisation:n:step:set:abstract}a-c)}.
 %
